
```{r}
library(robin)
```

Load graphs

```{r}
cell.graph <- as_undirected(igraph::read_graph(file="./results/median_cell_graph.graphml", format="graphml"))
gene.graph <- as_undirected(igraph::read_graph(file="./results/median_gene_graph.graphml", format="graphml"))
cell.graph
```

Generate random robin graph objects

```{r}
cell.random <- random(graph=cell.graph)
gene.random <- random(graph=gene.graph)
```

Check robustness

```{r}
cell.proc <- robinRobust(graph=cell.graph, graphRandom=cell.random, method="leiden")
gene.proc <- robinRobust(graph=gene.graph, graphRandom=gene.random, method="leiden")
plot(cell.proc)
plot(gene.proc)
```

Some statistical tests

```{r}
robinFDATest(cell.proc)
robinFDATest(gene.proc)
```

The statistical test we reference in the paper is below - it is the Bayes Factor
for the null hypothesis where the two robin plot curves come from the same process.
These scores indicate very strong evidence agains the null hypothesis.

Intuitively, this means that our clusters found on our networks are robust to
random permutations.

```{r}
robinGPTest(cell.proc)
robinGPTest(gene.proc)
```







